|

### 2020-01-15 nontex/install/windows/fn_installations.Rmd
install latex atom clean options

>>>>

**Latex Package Option**

*clean* pattern

```{bash}
**/*.run.xml, **/*.aux, **/*.aux.bak, **/*.bbl, **/*.bcf, **/*.blg, **/*.dvi, **/*.fdb_latexmk, **/*.fls, **/*.idx, **/*.idx.bak, **/*.ilg, **/*.ind, **/*.lof, **/*.log, **/*.lol, **/*.lot, **/*.nav, **/*.out, **/*.ps, **/*.snm, **/*.synctex.gz, **/*.toc, /**/_minted-{jobname}, /{output_dir}/sage-plots-for-{jobname}.tex, /missfont.log, /texput.log, /texput.aux
```
